A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-28 notes/notes.tex
updated future goals

\documentclass[10pt]{report}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

@@

\subsection{On the Bethe lattice}
Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number). In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\). This allows a metal-insulator transition in the limit of $w\to\infty$ as well. In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}. This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy}. Applying the limit of \(w\to \infty\) on that equation gives
\begin{equation}\begin{aligned}
	&\Sigma_{H-H}(\omega) = \lim_{k\to \infty} G_0 -\\
	&\lim_{w \to \infty}\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\\
	& = \lim_{w\to \infty}\left[G_0(\omega) - G_\text{aux}(d_1,d_1;\omega)\right] 
\end{aligned}\end{equation}
It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.

\chapter{Future goals}
\begin{enumerate}
\item Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism. Compare with what is obtained from DMFT and its improvements. Also, determine the nature of the bath $\Sigma (k,\omega)$ for the transition point.

\item Once the zero temperature Mott metal-insulator transition is observed, we will investigate its nature.

\item While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final_siam} holds quite generally for the two-particle Greens function sector as well. We will provide these expressions at a later point in time. More specifically, we will calculate the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.

\item It is also important to benchmark the ground state energy and double occupancy obtained from this method against the ground state wavefunction obtained from exact diagonalisation of small lattices and finite size scaling.

\item It should also prove instructive to investigate the nature of many-particle entanglement in the ground state wavefunction of various phases, and  look for signs of a quantum liquid.

@@

\item This method can also be extended to various other models of strong correlation:
	\begin{enumerate}
		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
		\item Hubbard-Heisenberg model, by starting from a generalized Anderson molecule (Anderson molecule with two-particle spin and charge interactions between the two sites)
	\end{enumerate}
\end{enumerate}

@@

\chapter{Derivation of RG equations: \(U_b\)-free terms}
\section{Renormalisation of the impurity energy \(\epsilon_d\)}
The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\). We will consider these processes one after another. We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step. In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes. The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom. We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations. The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\). To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\). This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state. Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).

@@

\section{Renormalisation of the hybridisation \(V\)}
Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\). In order words, the two vertices involve one single-particle scattering and one spin or isospin exchange respectively. We first look at the vertices that involve a spin-exchange scattering.

@@

\section{Renormalisation of the exchange couplings \(J\) and \(K\)}
We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry. The terms that renormalise \(J^z\) are of the form \(S_d^\pm S_d^\mp\). In the particle sector, we have
\begin{equation}\begin{aligned}
	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} \frac{1}{\omega - H_D}S_d^\mp c^\dagger_{k\pm}c_{q\mp} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2} \pm S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
\end{aligned}\end{equation}
The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
In the hole sector, we similarly have
\begin{equation}\begin{aligned}
	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\mp c^\dagger_{k\pm}c_{q\mp} \frac{1}{\omega - H_D}S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} = n_j \frac{1}{4}J^2 \left(\frac{1}{2} \mp S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
\end{aligned}\end{equation}
Adding all four expressions and dropping the constant part, we get
\begin{equation}\begin{aligned}
	-n_j \frac{1}{2}J^2 S_d^z \sum_{kk^\prime}\left(c^\dagger_{k \uparrow}c_{k^\prime \uparrow} - c^\dagger_{k \downarrow}c_{k^\prime \downarrow}\right) \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
\end{aligned}\end{equation}
We can now directly read off the RG equation for \(J\):
\begin{equation}\begin{aligned}
	\Delta J = -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}

@@

\chapter{Derivation of RG equations: \(U_b\)-included terms}

@@

\section{Renormalisation of \(U_b\)}
\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
\begin{equation}\begin{aligned}
	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
\end{aligned}\end{equation}
In order to renormalise \(U_b\), we need to contract one more pair of momenta. There are two choices. The first is by setting \(k_3 = k_3^\prime = q\). The two internal states, then, are \(q\beta\) and \(q\overline\beta\). As discussed above, the intermediate state energy is \(-U_b/4\). We therefore have
\begin{equation}\begin{aligned}
	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
\end{aligned}\end{equation}
Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
\begin{equation}\begin{aligned}
	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
\end{aligned}\end{equation}
The two contributions cancel each other. The same cancellation happens in the hole sector as well.

\section{Renormalisation of \(U\)}
\(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
\begin{equation}\begin{aligned}
	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)~.
\end{aligned}\end{equation}
On accounting for the contribution of \(U_b\) to the denominator, we get
\begin{equation}\begin{aligned}
	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right)~.
\end{aligned}\end{equation}

\section{Renormalisation of \(V\)}
The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
\begin{equation}\begin{aligned}
	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} \\
	&= n_jU_b V\sum_{k\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c^\dagger_{d\beta}
\end{aligned}\end{equation}
\(E_1\) and \(E_0\) are the intermediate state energies for \(\hat n_{d\overline\beta}=1\) and 0 respectively. \(\omega_{1,0}\) are the quantum fluctuation scales for the corresponding initial states. \(\omega^\prime_{1,0}\) are the fluctuation scales for the corresponding final states.
The intermediate energies are \(E_1 = D/2 - U_b/4 - K/4,~ ~ ~ E_0 = D/2 - U_b/4 - U/2 - J/4\). The fluctuation scales are \(\omega_1 = \omega - U/2= \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega = \omega_0\). Substituting these gives
\begin{equation}\begin{aligned}
	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
+\left. \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
\end{aligned}\end{equation}

@@

\section{Renormalisation of \(J\) and \(K\)}
We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
\begin{equation}\begin{aligned}
	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
\end{aligned}\end{equation}
The factor of half in front is the same half factor that appears in front of the \(S_1^+ S_2^-, S_1^-S_2^+\) terms when we rewrite \(\vec{S}_1\cdot\vec{S}_2\) in terms of \(S^z, S^\pm\). Another term is obtained by switching \(J\) and \(U_b\):
\begin{equation}\begin{aligned}
	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
\end{aligned}\end{equation}

>>>>

\documentclass[10pt]{report}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,pifont,enumitem}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\newcommand{\cmark}{\ding{51}}%

@@

\subsection{On the Bethe lattice}
Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number). In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\). This allows a metal-insulator transition in the limit of $w\to\infty$ as well. In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}. This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy}. Applying the limit of \(w\to \infty\) on that equation gives
\begin{equation}\begin{aligned}
	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G_\text{aux}^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
	&\left.\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\right\}\\
	& = \lim_{w\to \infty}\left\{G_\text{aux}^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
\end{aligned}\end{equation}
where \(G_\text{aux}^{(0)}(\vec k,\omega)\) is the non-interacting Greens function. It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.

\chapter{Future goals}
\begin{enumerate}
\item The Mott metal-insulator transition:
	\begin{todolist}
	\item[\cmark] Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
	\end{todolist}

\item Higher-order Greens functions:
	\begin{todolist}
	\item Provide expressions for two-particle Greens functions.
	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
	\item Obtain spectral functions for such excitations
	\end{todolist}

\item Benchmarking against ED and/or finite size scaling:
	\begin{todolist}
	\item ground state energy
	\item double occupancy
	\end{todolist}

\item Upgrade to two-site cluster:
	\begin{todolist}
	\item Study a two-impurity model under renormalisation group
	\item[\cmark] Derive the tiling and Greens function relations for such a two-impurity model 
	\item Demonstrate Mott MIT here.
	\item Investigate the nature of many-particle entanglement in such a cluster
	\item look for signs of a quantum liquid.
	\end{todolist}

@@

\item This method can also be extended to various other models of strong correlation:
	\begin{enumerate}
		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
	\end{enumerate}
\end{enumerate}

@@

\chapter{Derivation of RG equations}
\section{\(U_b\)-free terms}
\subsection{Renormalisation of the impurity energy \(\epsilon_d\)}
The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\). We will consider these processes one after another. We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step. In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes. The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom. We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations. The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\). To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\). This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state. Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).

@@

\subsection{Renormalisation of the hybridisation \(V\)}
Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\). In order words, the two vertices involve one single-particle scattering and one spin or isospin exchange respectively. We first look at the vertices that involve a spin-exchange scattering.

@@

\subsection{Renormalisation of the exchange couplings \(J\) and \(K\)}
We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry. The terms that renormalise \(J^z\) are of the form \(S_d^\pm S_d^\mp\). In the particle sector, we have
\begin{equation}\begin{aligned}
	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} \frac{1}{\omega - H_D}S_d^\mp c^\dagger_{k\pm}c_{q\mp} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2} \pm S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
\end{aligned}\end{equation}
The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
In the hole sector, we similarly have
\begin{equation}\begin{aligned}
	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\mp c^\dagger_{k\pm}c_{q\mp} \frac{1}{\omega - H_D}S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} = n_j \frac{1}{4}J^2 \left(\frac{1}{2} \mp S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
\end{aligned}\end{equation}
Adding all four expressions and dropping the constant part, we get
\begin{equation}\begin{aligned}
	-n_j \frac{1}{2}J^2 S_d^z \sum_{kk^\prime}\left(c^\dagger_{k \uparrow}c_{k^\prime \uparrow} - c^\dagger_{k \downarrow}c_{k^\prime \downarrow}\right) \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
\end{aligned}\end{equation}
We can now directly read off the RG equation for \(J\):
\begin{equation}\begin{aligned}
	\Delta J = -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}

@@

\section{\(U_b\)-included terms}

@@

\subsection{Renormalisation of \(U_b\)}
\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
\begin{equation}\begin{aligned}
	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
\end{aligned}\end{equation}
In order to renormalise \(U_b\), we need to contract one more pair of momenta. There are two choices. The first is by setting \(k_3 = k_3^\prime = q\). The two internal states, then, are \(q\beta\) and \(q\overline\beta\). As discussed above, the intermediate state energy is \(-U_b/4\). We therefore have
\begin{equation}\begin{aligned}
	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
\end{aligned}\end{equation}
Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
\begin{equation}\begin{aligned}
	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
\end{aligned}\end{equation}
The two contributions cancel each other. The same cancellation happens in the hole sector as well.

\subsection{Renormalisation of \(U\)}
\(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
\begin{equation}\begin{aligned}
	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)~.
\end{aligned}\end{equation}
On accounting for the contribution of \(U_b\) to the denominator, we get
\begin{equation}\begin{aligned}
	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right)~.
\end{aligned}\end{equation}

\subsection{Renormalisation of \(V\)}
The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
\begin{equation}\begin{aligned}
	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} \\
	&= n_jU_b V\sum_{k\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c^\dagger_{d\beta}
\end{aligned}\end{equation}
\(E_1\) and \(E_0\) are the intermediate state energies for \(\hat n_{d\overline\beta}=1\) and 0 respectively. \(\omega_{1,0}\) are the quantum fluctuation scales for the corresponding initial states. \(\omega^\prime_{1,0}\) are the fluctuation scales for the corresponding final states.
The intermediate energies are \(E_1 = D/2 - U_b/4 - K/4,~ ~ ~ E_0 = D/2 - U_b/4 - U/2 - J/4\). The fluctuation scales are \(\omega_1 = \omega - U/2= \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega = \omega_0\). Substituting these gives
\begin{equation}\begin{aligned}
	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
+\left. \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
\end{aligned}\end{equation}

@@

\subsection{Renormalisation of \(J\) and \(K\)}
We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
\begin{equation}\begin{aligned}
	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
\end{aligned}\end{equation}
The factor of half in front is the same half factor that appears in front of the \(S_1^+ S_2^-, S_1^-S_2^+\) terms when we rewrite \(\vec{S}_1\cdot\vec{S}_2\) in terms of \(S^z, S^\pm\). Another term is obtained by switching \(J\) and \(U_b\):
\begin{equation}\begin{aligned}
	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
\end{aligned}\end{equation}
